What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Correct percentage of V for which eval was actually useful

\medskip\noindent\EE{$min(e)=\c{V}$} Expressions that represent values are
frequently passed to \eval -- they occur in 17\% of sites. The majority of
those, \packageValOneNodePercent, are inline constants (integer or double
vectors). The rest trivially evaluate to a value, \eg~\c{1+1}.\footnote{True as
long as base functions such as \c{+} are not redefined. They typically aren't,
but this is a limitation of this categorization.} In our corpus,
\packageNbCallSitesUniqueActualValue call sites only ever see a simple value.
Manual inspection reveals cases such as the following
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
where the argument to \eval is a string which \eval simply returns. From twenty
randomly selected \evals, \packageUsefulValueEvalPercent of them do not need
\eval. For the other cases, either we are dealing with a value that needs to be
constructed dynamically or the value is a default case that sometimes is
replaced by a more interesting expression. This form is usually evaluated in few
interpreter steps, in fact the median is only
\packageMinimizedmedianoperationscRnd. The environment in which they evaluate is
mostly irrelevant (unless a built-in operator is redefined).

@@

\mypara{Function definition.} This corresponds to minimized expression \c{FUN}. Package \emph{Rcpp} is used to easily interface C++ and R and it uses \eval to bind C++ functions and classes to R objects.
For instance, \c{.makeCppMethods} create a R function for each C++ method named \c{what} of a given class.
\begin{lstlisting}
methods[[what]] <- eval(substitute(
	function(...) .CppObject$WHAT(...), list(WHAT = as.name(what))),
	env)
\end{lstlisting}

@@

In the R community, the call capturing pattern is often referred~\cite{hadley} as \emph{Non-Standard Evaluation}.

>>>>

\medskip\noindent\EE{$min(e)=\c{V}$} Expressions that represent values are
frequently passed to \eval -- they occur in 17\% of sites. The majority of
those, \packageValOneNodePercent, are inline constants (integer or double
vectors). The rest trivially evaluate to a value, \eg~\c{1+1}.\footnote{True as
long as base functions such as \c{+} are not redefined. They typically aren't,
but this is a limitation of this categorization.} In our corpus,
\packageNbCallSitesUniqueActualValue call sites only ever see a simple value.
Manual inspection reveals cases such as the following
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
where the argument to \eval is a string which \eval simply returns. From twenty
randomly selected \evals, \packageUsefulValueEvalPercent of them  need % There are a majority which needs eval
\eval for some inputs. Either we are dealing with a value that needs to be
constructed dynamically or the value is a default case that sometimes is
replaced by a more interesting expression. This form is usually evaluated in few
interpreter steps, in fact the median is only
\packageMinimizedmedianoperationscRnd. The environment in which they evaluate is
mostly irrelevant (unless a built-in operator is redefined).

@@

\mypara{Function definition.} This corresponds to minimized expression \c{FUN}. Package \emph{Rcpp} is used to easily interface C++ and R and it uses \eval to bind C++ functions and classes to R objects.
For instance, \c{.makeCppMethods} create a R function for each C++ method named \c{what} of a given class. The use of \substitute to inject the name of the method in a language expression entails the use of \eval.
\begin{lstlisting}
methods[[what]] <- eval(substitute(
	function(...) .CppObject$WHAT(...), list(WHAT = as.name(what))),
	env)
\end{lstlisting}

\mypara{Block.} %injecting pre nad post processing

@@

In the R community, the call capturing pattern with evaluation in a non-local environment is often referred~\cite{hadley} as \emph{Non-Standard Evaluation}.
